Title Goes Here

### 2023-10-29 paper/main.tex
updates to evaluation

\maketitle

@@

\begin{table}
\centering
  \begin{tabular}{|l | l|l|}
    \hline
    \textbf{Protocol} & \textbf{Purpose} & \textbf{Ref.} \\
    \hline
    $n$-bit Addition & Custom & TODO \\
    Oblivious Transfer & Building block & TODO \\
    OT Extension & Building block & TODO \\
    Beaver Triple Generation & Building block & TODO \\
    GMW & Circuit evaluation & TODO \\
    MPC w/ Beaver Triples & Circuit evaluation & TODO \\
    \hline
  \end{tabular}
  \caption{Secure protocols used in our evaluation.}
  \label{tbl:protocols}
\end{table}

@@

\paragraph{Oblivious Transfer.}
Oblivious transfer~\cite{todo} (OT) is a 2-party protocol that allows one party ($R$, the \emph{receiver}) to select one out of several secret inputs provided by the other party ($S$, the \emph{sender}). In 1-out-of-2 OT, $S$ provides 2 secret inputs $x_0$ and $x_1$ and $R$ provides a secret \emph{selection bit} $b$. If $b=0$, $R$ receives $x_0$; if $b=1$, $R$ receives $x_1$. $R$ does not learn anything about the not-selected secret, and $S$ does not learn which secret $R$ selected. This idea can be extended to 1-out-of-$n$ OT by extending the selection bit $b$ to a $\log_2(n)$-bit string.
%
Oblivious transfer is a building block for many other protocols. For example, the GMW protocol for circuit evaluation (described later) evaluates AND gates using 1-out-of-4 OT

\paragraph{Oblivious Transfer Extension.}
Protocols like GMW (described later) require the use of OT for each AND gate---for large circuits, this means thousands or millions of OTs. \emph{OT extension}~\cite{todo} is an approach for expanding $k$ ``base'' OTs into $m \gg k$ OTs. OT extension can significantly improve the performance of protocols that use many OTs.

@@

\paragraph{GMW (Goldreich-Micali-Widgerson.}

\paragraph{MPC with Beaver Triples.}

\paragraph{Circuits.}
To evaluate the circuit-based protocols, we used five binary circuits that are publicly available in the ``Bristol-fashion'' format~\cite{todo}. We chose commonly-used circuits with a range of sizes to test \system's scalability. Table~\ref{tbl:circuits} lists the circuits used in our evaluation, along with the number of gates in each circuit.

\begin{table}
\centering
  \begin{tabular}{|l |l|l|}
    \hline
    \textbf{Circuit} & \textbf{AND Gates} & \textbf{Total Gates} \\
    \hline
    64-bit adder & 63 & 376 \\
    64-bit multiplier & 4,033 & 13,675 \\
    AES-128 & 6,400 & 36,663 \\
    SHA-256 & 22,573 & 135,073 \\
    Floating-point division & 82,269 & 184,007 \\
    \hline
  \end{tabular}
  \caption{Circuits used in our evaluation.}
  \label{tbl:circuits}
\end{table}

@@

\subsection{Experiment 1: Scalability for Secure Protocols}

\subsection{Experiment 2: Bug-Finding for Insecure Protocol Mutations}

\subsection{Experiment 3: Scalability and Bug-Finding for Random Programs}

>>>>

\maketitle
\thispagestyle{plain}
\pagestyle{plain}

@@

\begin{table}
\centering
  \begin{tabular}{|l | l|l|}
    \hline
    \textbf{Protocol} & \textbf{Purpose} & \textbf{Ref.} \\
    \hline
    $n$-bit Addition & Custom & TODO \\
    Oblivious Transfer & Building block & TODO \\
%    OT Extension & Building block & TODO \\
    Beaver Triple Generation & Building block & TODO \\
    GMW & Circuit evaluation & TODO \\
    MPC w/ Beaver Triples & Circuit evaluation & TODO \\
    \hline
  \end{tabular}
  \caption{Secure protocols used in our evaluation.}
  \label{tbl:protocols}
\end{table}

@@

\paragraph{Oblivious Transfer.}
Oblivious transfer~\cite{todo} (OT) is a 2-party protocol that allows one party ($R$, the \emph{receiver}) to select one out of several secret inputs provided by the other party ($S$, the \emph{sender}). In 1-out-of-2 OT, $S$ provides 2 secret inputs $x_0$ and $x_1$ and $R$ provides a secret \emph{selection bit} $b$. If $b=0$, $R$ receives $x_0$; if $b=1$, $R$ receives $x_1$. $R$ does not learn anything about the not-selected secret, and $S$ does not learn which secret $R$ selected. This idea can be extended to 1-out-of-$n$ OT by extending the selection bit $b$ to a $\log_2(n)$-bit string.
%
Oblivious transfer is a building block for many other protocols.

% \paragraph{Oblivious Transfer Extension.}
% Protocols like GMW (described later) require the use of OT for each AND gate---for large circuits, this means thousands or millions of OTs. \emph{OT extension}~\cite{todo} is an approach for expanding $k$ ``base'' OTs into $m \gg k$ OTs. OT extension can significantly improve the performance of protocols that use many OTs.

@@

\paragraph{GMW (Goldreich-Micali-Widgerson).}
The GMW protocol is an MPC protocol for evaluating circuits. Each party holds additive secret shares of each wire's value, and evaluates addition gates by adding the shares they hold. The parties evaluate multiplication gates by using 1-out-of-4 oblivious transfer: the first party generates a random bit for its share of the output, and acts as the sender in OT; the second party acts as the receiver in OT and receives its share of the output. We implemented a compiler to generate \system programs that evaluate  Bristol fashion circuits using GMW, and evaluated it on circuits implementing integer addition and integer inequalities.

\paragraph{MPC with Beaver Triples.}
Another MPC protocol for evaluating circuits also uses additive shares to hold wire values, but uses Beaver triples to evaluate multiplication gates (instead of OT). Given shares of a Beaver triple, the parties perform two multiplication-by-constant and broadcast operations, and derive one share each of the product. Our implementation of this approach employees a third-party ``dealer'' who generates the triples; a pre-processing (offline) phase can also be used to generate the triples. We evaluate \system on this protocol using the same circuits as in our GMW experiments.

% \paragraph{Circuits.}
% To evaluate the circuit-based protocols, we used five binary circuits that are publicly available in the ``Bristol-fashion'' format~\cite{todo}. We chose commonly-used circuits with a range of sizes to test \system's scalability. Table~\ref{tbl:circuits} lists the circuits used in our evaluation, along with the number of gates in each circuit.

% \begin{table}
% \centering
%   \begin{tabular}{|l |l|l|}
%     \hline
%     \textbf{Circuit} & \textbf{AND Gates} & \textbf{Total Gates} \\
%     \hline
%     64-bit adder & 63 & 376 \\
%     64-bit multiplier & 4,033 & 13,675 \\
%     AES-128 & 6,400 & 36,663 \\
%     SHA-256 & 22,573 & 135,073 \\
%     Floating-point division & 82,269 & 184,007 \\
%     \hline
%   \end{tabular}
%   \caption{Circuits used in our evaluation.}
%   \label{tbl:circuits}
% \end{table}

@@

\begin{itemize}
\item \textbf{RQ1:} Is \system capable of detecting insecurity in complex, multi-round protocols?
\item \textbf{RQ2:} Is \system capable of detecting insecurity in real-world protocols?
\end{itemize}

\subsection{Experiment 1: Real-world Secure Protocols}

\subsection{Experiment 2: Random Protocols}
